Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-20 paper/ms.tex
terminology related to #71

For a GP kernel to be valid, it must produce a positive definite covariance
matrix for all input coordinates.
For stationary kernels, this is equivalent~--~by Bochner's theorem \citep[see
Section 4.2.1 in][]{Rasmussen:2006}~--~to requiring that the kernel be the
Fourier transform of a positive finite measure.
This means that the power spectrum of a positive definite kernel must be
positive for all frequencies.  This seems true intuitively:  since the
power spectrum is the square of the Fourier transform of the data time
series, it must be non-negative.

>>>>

For a GP kernel to be valid, it must produce a positive definite covariance
matrix for all input coordinates.
For stationary kernels, this is equivalent~--~by Bochner's theorem \citep[see
Section 4.2.1 in][]{Rasmussen:2006}~--~to requiring that the kernel be the
Fourier transform of a positive finite measure.
This means that the power spectrum of a positive definite kernel must be
positive for all frequencies.
This result is also intuitive because, since the power spectrum of a process
is defined as expected the squared amplitude of the Fourier transform of the
time series, it must be non-negative.
